Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-26 Article_B7/Article_B7_plain.tex
Commit 2024-06-26 09:15

  \title{Long-term cloud enhancement events of global solar irradiance
over Thessaloniki, Greece}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  }
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  }
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

  \begin{abstract}
  Here will be the abstract.
  \end{abstract}
    \begin{keyword}
    cloud enhancement \sep total solar radiation \sep global horizontal
irradiance \sep 
    over irradiance
  \end{keyword}

@@

\section*{Abstract}\label{abstract}
\addcontentsline{toc}{section}{Abstract}

We studied the enhancement of the global horizontal irradiance induced
by clouds over Thessaloniki for the period 1993 -- 2023 using data
recorded every one minute. We identified the cloud enhancement events
(CE) by creating an appropriate clear sky irradiance reference with the
use of a radiative transfer model and aerosol optical depth data from a
collocated Cimel sun photometer and a Brewer spectrophotometer. We found
a trend in CE events of \(45.6\pm
21.9\,\text{cases}/\text{year}\), and a trend in the CE events
irradiation of \(116.9\pm
67.8\,\text{kJ}/\text{year}\). The peak of the CE events was observed
during May and June. An analysis of the total duration of CE events,
showed that durations longer than 5 minutes are very rare, with
exceptions lasting over an hour and up to 140 minutes. Finally, we have
detected enhancements above the total solar irradiance at the top of the
atmosphere of up to \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\)
of the cases below \(200\,\text{W}/\text{m}^{2}\). The most active
season of these extreme events is spring until early summer and autumn.

\section{Introduction}\label{introduction}

@@

\section{Data and methodology}\label{data-and-methodology}

\subsection{Instrumentation and data}\label{instrumentation-and-data}

@@

\subsection{Cloud enhancement
detection}\label{cloud-enhancement-detection}

@@

\subsection{Modeled clear Sky Irradiance}\label{rtmcs}

\subsubsection{Climatology of clear sky
irradiance}\label{climatology-of-clear-sky-irradiance}

@@

\subsubsection{Long-term change of clear sky
irradiance}\label{long-term-change-of-clear-sky-irradiance}

@@

\subsection{Criteria for the identification of CE
events}\label{criteria-for-the-identification-of-ce-events}

@@

\section{Results}\label{results}

@@

\subsection{Long-term trends}\label{long-term-trends}

@@

\subsection{Climatology of cloud enhancement
events}\label{climatology-of-cloud-enhancement-events}

@@

\subsection{Duration of cloud enhancement
events}\label{duration-of-cloud-enhancement-events}

@@

\subsection{Extreme cloud enhancement
events}\label{extreme-cloud-enhancement-events}

@@

\section{Conclusions}\label{conclusions}

By creating a clear sky approximation of the GHI, which represents the
long- and short-term variation of the expected clear sky GHI, we were
able to identify cases of CE events. After analyzing the CE cases, we
found an increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\), with
the mean annual total energy of the CE events increasing with a rate of
\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active season of CE
events over Thessaloniki is concentrated on early summer, on May and
June. We found that continuous CE events can last up to \(140\) minutes,
and \(80\,\\%\) of them bellow \(5\) minutes.

>>>>

  \title{Long-term cloud enhancement events of global solar irradiance
over Thessaloniki, Greece}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  }
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  }
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  We studied the enhancement of the global horizontal irradiance induced
  by clouds over Thessaloniki for the period 1993 -- 2023 using data
  recorded every one minute. We identified the cloud enhancement events
  (CE) by creating an appropriate clear sky irradiance reference with
  the use of a radiative transfer model and aerosol optical depth data
  from a collocated Cimel sun photometer and a Brewer spectrophotometer.
  We found a trend in CE events of
  \(45.6\pm 21.9\,\text{cases}/\text{year}\), and a trend in the CE
  events irradiation of \(116.9\pm 67.8\,\text{kJ}/\text{year}\). The
  peak of the CE events was observed during May and June. An analysis of
  the total duration of CE events, showed that durations longer than 5
  minutes are very rare, with exceptions lasting over an hour and up to
  140 minutes. Finally, we have detected enhancements above the total
  solar irradiance at the top of the atmosphere of up to
  \(400\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the cases below
  \(200\,\text{W}/\text{m}^{2}\). The most active season of these
  extreme events is spring until early summer and autumn.
  \end{abstract}
    \begin{keyword}
    cloud enhancement \sep total solar radiation \sep global horizontal
irradiance \sep 
    over irradiance
  \end{keyword}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{data-and-methodology}{%
\section{Data and methodology}\label{data-and-methodology}}

\hypertarget{instrumentation-and-data}{%
\subsection{Instrumentation and data}\label{instrumentation-and-data}}

@@

\hypertarget{cloud-enhancement-detection}{%
\subsection{Cloud enhancement
detection}\label{cloud-enhancement-detection}}

@@

\hypertarget{rtmcs}{%
\subsection{Modeled clear Sky Irradiance}\label{rtmcs}}

\hypertarget{climatology-of-clear-sky-irradiance}{%
\subsubsection{Climatology of clear sky
irradiance}\label{climatology-of-clear-sky-irradiance}}

@@

\hypertarget{long-term-change-of-clear-sky-irradiance}{%
\subsubsection{Long-term change of clear sky
irradiance}\label{long-term-change-of-clear-sky-irradiance}}

@@

\hypertarget{criteria-for-the-identification-of-ce-events}{%
\subsection{Criteria for the identification of CE
events}\label{criteria-for-the-identification-of-ce-events}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{long-term-trends}{%
\subsection{Long-term trends}\label{long-term-trends}}

@@

\hypertarget{climatology-of-cloud-enhancement-events}{%
\subsection{Climatology of cloud enhancement
events}\label{climatology-of-cloud-enhancement-events}}

@@

\hypertarget{duration-of-cloud-enhancement-events}{%
\subsection{Duration of cloud enhancement
events}\label{duration-of-cloud-enhancement-events}}

@@

\hypertarget{extreme-cloud-enhancement-events}{%
\subsection{Extreme cloud enhancement
events}\label{extreme-cloud-enhancement-events}}

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

By creating a clear sky approximation of the GHI, which represents the
long- and short-term variation of the expected clear sky GHI, we were
able to identify cases of CE events. After analyzing the CE cases, we
found an increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\), with
the mean annual total energy of the CE events increasing with a rate of
\(116.9\pm 67.8\,\text{kJ}/\text{year}\). The most active season of CE
events over Thessaloniki is concentrated on early summer, on May and
June. We found that continuous CE events can last up to \(140\) minutes,
and \(80\,\%\) of them bellow \(5\) minutes.
